---
title: "Supplementary Material: Operating-model conditioning"
subtitle: "Shared text and FLBacktest workflow for peer-reviewed papers"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
  word_document:
    toc: true
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      eval = FALSE)
```

# Purpose

This note documents the **shared** conditioning steps used by papers that run
historical HCR backtests with **FLBacktest**. Application repositories supply
stock-specific assessments, reference points, and scenario labels; the package
supplies the reusable helpers below.

Host papers should `\input` or child-document this file (or copy the prose into
a LaTeX supplement) and replace the placeholders with case-study detail.

# Conditioning pipeline

1. Build an age-structured operating model (`FLStock`) from the assessment
   (or a set of plausible assessments).
2. Ensure projection slots are complete for `FLasher` (catch, landings,
   discards, weights, maturity, natural mortality, selectivity).
3. Fit a stock–recruitment relationship and represent it as an `FLBRP`
   equilibrium for short-term forecasts and closed-loop projections.
4. Derive HCR parameters (`FLPar`) from advice-year reference points.
5. Optionally expand epistemic uncertainty (assessment iters, alternative \(M\),
   recruitment regimes) and build multiplicative recruitment deviations.

# Package helpers

```{r helpers}
library(FLCore)
library(FLBRP)
library(FLBacktest)

## HCR parameters from reference-point series (FLQuants or named list)
## Expected names: fmsy / ftar, msybtrigger / btrig, blim
# par <- hcrParams(refs)

## Mass-based natural mortality (optional OM hypothesis)
# m(om) <- lorenzenM(om)

## Assessment uncertainty iters via FLfse (requires Suggested packages)
# omU <- omIters(om, n = 100)

## Recruitment deviations (AR(1) about lowess; optional epistemic trend)
# rsd <- recDevs(residuals(sr), nits = 100, trend = FALSE)
# sr_deviances <- exp(rsd)

## Leave-one-out SR residuals (diagnostics / alternative deviations)
# loo <- looResiduals(sr)
```

# What the application must supply

| Object | Role |
|--------|------|
| `om` / `omIters` | Conditioned `FLStock` (possibly multi-iter or multi-OM list) |
| `eq` / `eqs` | Fitted `FLBRP` (or named list by OM / regime) |
| `refs` → `params` | Advice-year \(F_{\mathrm{MSY}}\), \(MSYB_{\mathrm{trigger}}\), \(B_{\lim}\) |
| `sr_deviances` | Multiplicative recruitment process for the backtest window |
| Scenario grid | Optional `data.frame` of OM × regime (or other factors) for `backtest()` |

# Case-study checklist (fill in host paper)

- Assessment software and terminal year(s)
- Historical conditioning window and any structural breaks (benchmarks)
- Natural mortality hypotheses retained as OMs
- Stock–recruit form(s) and how residuals enter the closed loop
  (aleatory vs epistemic)
- Source of reference points (SAG, advice sheets, assessment report)

# Software

Conditioning uses FLR (`FLCore`, `FLBRP`) and **FLBacktest** helpers
`hcrParams()`, `lorenzenM()`, `omIters()`, `recDevs()`, and
`looResiduals()`. Full SAM uncertainty expansion additionally requires
**FLfse** / **stockassessment**.
