---
title: "Supplementary Material: Observation and estimation error"
subtitle: "Shared OEM text and FLBacktest workflow for peer-reviewed papers"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
  word_document:
    toc: true
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      eval = FALSE)
```

# Purpose

This note documents the three nested **observation / estimation models**
(OEMs) available in **FLBacktest** for historical HCR backtests. Papers state
which OEM is the base case and which are sensitivities.

# OEM hierarchy

| Mode | `err` argument | What the MP perceives |
|------|----------------|------------------------|
| Perfect information | `NULL` | True OM status and STF with rec. deviations |
| Short-cut | `FLQuant` of multiplicative bias | OM status × assessment error |
| Full feedback | `FLIndex` (age / SSB / Rec) | Status from a yearly re-assessment |

All three feed the same HCR (`hcrICES` / `backtest`); only the perceive step
changes. `err = NULL` is perfect information — there is no separate
`perfect` argument.

# Perfect information

```{r perfect}
library(FLBacktest)

# res <- backtest(om, eq, sr_deviances = exp(rsd), params = par,
#                 method = "perfect", err = NULL,
#                 start = start, end = end)
```

Use perfect information to isolate HCR geometry and implementation from
assessment error. It is **not** a realistic advice process.

# Short-cut assessment error

Retrospective peels supply empirical `now`/`then` bias ratios. An ARIMA
(or AR(1) fallback) model is fitted and simulated across years and
iterations to build a multiplicative error `FLQuant`.

```{r shortcut}
## From a list of FLStocks peels (or FLStocks) keyed by OM
# bias_df <- retroBias(retros)
# biasSummary(bias_df)   # optional diagnostic table

## Simulate error for one OM over the backtest window
# err <- shortcut(bias_df, id = "base", start = start, end = end, nits = 100)

# res <- backtest(om, eq, sr_deviances = exp(rsd), params = par,
#                 method = "shortcut", err = err,
#                 start = start, end = end)
```

Aliases: `shortCutErr()`, `biasFromRetros()`. Prefer the **forecast** package
for ARIMA; otherwise FLBacktest uses an AR(1) approximation.

# Full feedback (assessment-based MP)

Each advice year the MP re-fits (or updates) an assessment on catch and survey
data contemporaneous with \(t\), then applies the HCR to assessment estimates.
Indices are built from the OM with observation noise.

```{r full}
## Age-structured or aggregated indices for SAM / FLfse
# idx  <- samIndex(om)          # or samIndexSSB(om), samIndexRec(om)
# validateSamIndex(idx)

# res <- backtest(om, eq, sr_deviances = exp(rsd), params = par,
#                 method = "full", err = idx,
#                 start = start, end = end,
#                 wgName = "base")   # scenario-grid / naming helper when used
```

Full feedback requires Suggested packages **FLfse** and **stockassessment**.

# Case-study checklist (fill in host paper)

- Base-case OEM and sensitivity OEMs
- Peel design (years, software, validation against published assessments)
- Short-cut: metric biased (usually SSB), ARIMA order / AR(1), iteration count
- Full: survey construction, CV / noise model, assessment configuration
  used inside the loop
- Any estimation natural mortality that differs from the OM

# Software

OEM construction uses **FLBacktest** `retroBias()`, `shortcut()`,
`samIndex*()`, and `validateSamIndex()`. Closed-loop application is via
`backtest(..., method = "perfect"|"shortcut"|"full")` or direct `hcrICES()`.
