---
title: "Supplementary Material: Management procedure"
subtitle: "Shared HCR / closed-loop text and FLBacktest workflow"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
  word_document:
    toc: true
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      eval = FALSE)
```

# Purpose

This note documents the shared **management procedure** (MP): the ICES-style
hockey-stick harvest control rule (HCR) embedded in a year-by-year historical
closed loop. Implementation lives in **FLBacktest**; papers state reference
points, lags, TAC bounds, and the OEM used with the HCR.

# Perceive → advise → implement

For each advice year \(t\) in \([t_0, T]\):

1. **Perceive** stock status under the chosen OEM (perfect, short-cut, or full).
2. **Advise** catch (or \(F\)) with the HCR and reference points in force at \(t\).
3. **Implement** the advice on the OM with `FLasher`, optionally with
   implementation error and year-to-year TAC constraints.
4. Advance to \(t{+}1\) and repeat.

The result is a counterfactual trajectory under consistent adherence to advice
as understood at the time.

# Hockey-stick HCR

\[
F_{\mathrm{advice}}(B) =
\begin{cases}
0, & B \le B_{\lim}, \\[4pt]
F_{\min} + (F_{\mathrm{tar}} - F_{\min})\,
\dfrac{B - B_{\min}}{B_{\mathrm{trig}} - B_{\min}},
& B_{\lim} < B < B_{\mathrm{trig}}, \\[4pt]
F_{\mathrm{tar}}, & B \ge B_{\mathrm{trig}}.
\end{cases}
\]

Default mapping for ICES Category 1 advice:
\(F_{\mathrm{tar}} = F_{\mathrm{MSY}}\),
\(B_{\mathrm{trig}} = MSYB_{\mathrm{trigger}}\),
and \(B_{\lim}\) as published for year \(t\). Catch advice is obtained by
short-term projection of the *perceived* stock at \(F_{\mathrm{advice}}\).

HCR parameters are an `FLPar` with names `ftar`, `fmin`, `btrig`, `bmin`,
`blim` (build with `hcrParams()` from reference-point series).

# Package API

```{r mp}
library(FLBacktest)

## Single OM
# res <- hcrICES(om, eq,
#                sr_deviances = exp(rsd),
#                params = par,
#                start = start, end = end,
#                interval = 1, lag = 1,
#                err = NULL,              # or short-cut FLQuant / FLIndex
#                implErr = 0,
#                bndTac = c(0.8, 1.25),   # c(0, Inf) disables
#                bndWhen = "btrig")

## Same via backtest() with method switch
# res <- backtest(om, eq, sr_deviances = exp(rsd), params = par,
#                 method = "perfect",   # or "shortcut", "full"
#                 err = err,
#                 start = start, end = end,
#                 bndTac = c(0.8, 1.25))

## Scenario grid (parallel foreach when registered)
# scen <- expand.grid(om = names(eqs), regime = names(eqs[[1]]),
#                     stringsAsFactors = FALSE)
# out  <- backtest(scen, omIters = omIters, eqs = eqs,
#                  sr_deviances = exp(rsd), params = par,
#                  method = "shortcut", err = err,
#                  start = start, end = end, bndTac = c(0.8, 1.25))

## Thin wrappers (same engine)
# runMSE() / runShortCut() / runFull()
```

`hcrICES` / `backtest` return a `list`: projected `FLStock` and a
`data.frame` of HCR-tracked SSB, \(F\), and catch.

# Design rules for application papers

- Do **not** re-implement the hockey-stick loop locally; call `hcrICES` /
  `backtest`.
- Keep stock cleaning, SAG parsing, and case-study scenario labels in the
  application repository.
- Treat benchmark years as structural breaks when reference points change.
- State assessment lag, advice lag, and TAC stability rules explicitly.

# Case-study checklist (fill in host paper)

- Backtest window \([t_0, T]\) and advice interval
- Reference-point time series and benchmark breaks
- TAC bounds (`bndTac`) and when they apply (`bndWhen`)
- Implementation error hypothesis (none vs multiplicative)
- Perfect-management assumption (advised catch = realised catch in the OM)

# Software

Closed-loop MP: **FLBacktest** `hcrICES()`, `backtest()`, `runMSE()`,
`runShortCut()`, `runFull()`, with projections via **FLasher**.
