---
title: "Supplementary Material: Performance statistics"
subtitle: "Shared metrics text and FLBacktest trajectory extraction"
author: "Laurence Kell"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
  word_document:
    toc: true
---

```{r knitr, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      eval = FALSE)
```

# Purpose

This note documents the **shared** performance-statistic layer for historical
HCR backtests. **FLBacktest** extracts trajectories; application papers
aggregate status, risk, yield, and stability summaries (and any stock-specific
indices such as forage or ABI).

# Trajectory extraction

```{r extract}
library(FLBacktest)

## From a single backtest / hcrICES result (list) or projected FLStock
# trj <- backtestResults(res)
# # columns typically: year, iter, and metrics SSB, Recruits, Yield, F

## Custom metrics (named functions of FLStock)
# trj <- backtestResults(res, metrics = list(
#   SSB = ssb, F = fbar, Yield = catch
# ))
```

Compare **counterfactual** (closed-loop) trajectories with the **realised**
historical path over the same years, and across OEM / OM scenarios where
relevant.

# Core metric families

Papers using the shared backtest report at least:

| Family | Typical statistics |
|--------|-------------------|
| **Biological status** | Proportion of years (or probability across iters) with SSB \(< B_{\lim}\), SSB \(< MSYB_{\mathrm{trigger}}\) |
| **Exploitation** | \(F / F_{\mathrm{MSY}}\) (mean, time above / below 1) |
| **Yield** | Mean and cumulative catch over the backtest window |
| **Stability** | Average annual variation (AAV) in catch (and optionally in SSB) |
| **Risk trade-offs** | Joint summaries of yield versus \(P(B < B_{\lim})\) |

Define each statistic on the same years and iteration set for realised and
counterfactual series so differences are attributable to the MP path.

# Example aggregations (application-level)

```{r aggregate}
## Illustrative — keep thresholds and table layout in the host paper
# library(dplyr)
#
# status <- trj |>
#   group_by(scenario, iter) |>
#   summarise(
#     p_blim  = mean(SSB < blim,  na.rm = TRUE),
#     p_btrig = mean(SSB < btrig, na.rm = TRUE),
#     mean_F  = mean(F, na.rm = TRUE),
#     mean_C  = mean(Yield, na.rm = TRUE),
#     aav_C   = mean(abs(diff(Yield)) / Yield[-length(Yield)], na.rm = TRUE),
#     .groups = "drop"
#   )
```

AAV for a series \(x_t\) is commonly
\(\mathrm{AAV} = \frac{1}{T-1}\sum_t |x_{t+1}-x_t| / |x_t|\)
(omit zeros or use a stated alternative if catch is zero).

# Stock-specific extensions

Retain in the application repository (do not fork into FLBacktest unless
widely reusable):

- Ecosystem / forage indices
- Age-based indicators (e.g. ABI)
- Rebuild or recovery time statistics
- Traffic-light or ERP presentation rules

# Case-study checklist (fill in host paper)

- Years included in each statistic (full window vs post-burn-in)
- Reference points used for status (fixed terminal vs year-specific advice)
- Iteration pooling (median across iters, risk probabilities, etc.)
- Realised vs counterfactual pairing rules
- Any additional paper-specific indicators and their units

# Software

Trajectory extraction: **FLBacktest** `backtestResults()`. Status, risk, AAV,
and presentation tables are computed in the application from those
trajectories (and from the host paper's reference-point series).
